### 2025-07-21 download-football-data.qmd
20250721 - tweaks

@HoCombine provide a Data Dictionary for data from the combine at the following link: <https://nflreadr.nflverse.com/articles/dictionary_combine.html>

>>>>

@HoCombine provide a Data Dictionary for data from the NFL Combine at the following link: <https://nflreadr.nflverse.com/articles/dictionary_combine.html>

### 2025-07-21 getting-started.qmd
20250721 - tweaks

```{r}
convert_temperature <- function(temperature, unit = "F"){
  if(unit == "F"){ # if the input temperature(s) in Fahrenheit
    newtemp <- (temperature - 32) / (9/5)
  } else if(unit == "C"){ # if the input temperature(s) in Celsius
    newtemp <- (temperature * (9/5)) + 32
  }

  return(newtemp)
}
```

>>>>

```{r}
convert_temperature <- function(temperature, unit = "F"){ # specify the arguments and any defaults
  if(unit == "F"){ # if the input temperature(s) in Fahrenheit
    newtemp <- (temperature - 32) / (9/5)
  } else if(unit == "C"){ # if the input temperature(s) in Celsius
    newtemp <- (temperature * (9/5)) + 32
  }

  return(newtemp) # this is what is returned by the function
}
```
